Image restoration using dimensionality reduction in the Fourier domain

### 2011-06-17 project/Paper/paper.tex
+ Added subsections
Added modified flowchart dia. Insert flowchart into paper

In our implementation, we use several tweaks to improve performance or quality:
\begin{itemize}
\item We perform the Fourier transform and thresholding on image patches to allow an individual threshold per patch.
\item To avoid discontinuity at the boundary of the patches, we use a frame around the actual patch to capture more information. (Image \ref{fig:framing}) This frame is not filled in by the reconstructed patch from the Fourier step. The frames of adjacent patches are overlapping if the frame size is set to a value larger than zero. At the image boundaries, we replicate the outermost pixels to provide a sufficient frame.\end{itemize}
((( TODO )))
Describe your idea and how it was implemented to solve
  the problem. Survey the related work, giving credit where credit is
  due.

@@

@@

>>>>

In our implementation, we use several tweaks to improve performance or quality:
\begin{itemize}
\item We perform the Fourier transform and thresholding on image patches to allow an individual threshold per patch.
\item To avoid discontinuity (Image \ref{fig:boundaryArtifacts}) at the boundary of the patches, we use a frame around the actual patch to capture more information. (Image \ref{fig:framing}) This frame is not filled in by the reconstructed patch from the Fourier step. The frames of adjacent patches are overlapping if the frame size is set to a value larger than zero. At the image boundaries, we replicate the outermost pixels to provide a sufficient frame.\end{itemize}
((( TODO )))
Describe your idea and how it was implemented to solve
  the problem. Survey the related work, giving credit where credit is
  due.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{images/boundaryArtifact_noframe}
  \caption{Artifacts that occur without a frame (frame size = 0). The patches are recognizable in the reconstruction}
  \label{fig:boundaryArtifacts}
\end{figure}

@@

((( TODO: Plot missingPixel\% vs. accuracy (vs. speed?) )))
